Chemistry of fossil Pinus pollen and the effect of acetolysis

### 2020-12-07 manuscript.Rmd
moved notes section; changed title; adjusted RQs.

---
title: 'Viability of FTIR on fossil pollen'
date: '2020/02/04'
output:
  bookdown::pdf_document2:
    toc: false
    extra_dependencies: ["flafter"]
bibliography: references.bib
csl: biology-letters.csl
---

@@

# Chemistry of fossil Pinus pollen and the effect of acetolysis

## Abstract
200 words no abreviations/refs

@@

@@

Tiefer See:
- 1870-2010
- laminated sediments
- Pinus pollen

Tinner/Cesar cores:
Urio Quattrocchi (supra mediterranean) [@bisculmHoloceneVegetationFire2012]
Sa Curcurica (thermo mediterranean) [@beffaVegetationFireHistory2016]
Lago del Sangiatto (southern alps)

@@

The study of plant micro and macrofossil (spores, seed and pollen),recovered from lake sediments and peat bogs, is an integral part of Palaeoecology and Palaeobotany.
Pollengrains are resistant to the diagenetic processes that occur in the formation of sediments, bogs and other deposits, which makes pollen records 
an important tool to reconstruct past floristic, vegetational and environmental changes. 
EXAMPLES

RQs
i. Difference between fresh and fossil grains.
ii. effect of orientation and depth/age on chemistry
iii. difference to other species
    -> needs extracting of spectra from files (marking of grains on images)
    -> add another core

>>>>

---
title: 'Chemistry of fossil Pinus pollen and the effect of acetolysis'
date: '2020/02/04'
output:
  bookdown::pdf_document2:
    toc: false
    extra_dependencies: ["flafter"]
bibliography: references.bib
csl: biology-letters.csl
---

@@

# Abstract
200 words no abreviations/refs

@@

The study of plant micro and macrofossil (spores, seed and pollen), recovered from lake sediments and peat bogs, is an integral part of Palaeoecology and Palaeobotany.
Pollengrains are resistant to the diagenetic processes that occur in the formation of sediments, bogs and other deposits, which makes pollen records an important tool to reconstruct past floristic, vegetational and environmental changes. 
EXAMPLES

RQs
i. Difference between fresh and fossil grains.
i.i effect of orientation on chemistry
i.ii effect of depth/age on chemistry
ii Differences between cores

@@

Tiefer See [@theuerkaufEffectsChangesLand2015]:
- 1870-2010
- laminated sediments
- Pinus pollen

@@
